---
title: "Kinase Inhibitor Prediction Overview"
date: "`r Sys.Date()`"
output: word_document
fig_width: 10
params:
  predictions: NA
  RNAseq_data: NA
  model_id: NA
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

if (params$RNAseq_data == "NA") {
	source(here('functions.R'))
	RNAseq_data = read_delim('data/quant.sf') %>% convert_salmon_to_HGNC_TPM()
} else {
	RNAseq_data = params$RNAseq_data
}

if (params$predictions == "NA") {
	predictions = make_predictions(RNAseq_data)
} else {
	predictions = params$predictions
}

if (params$model_id == "NA") {
	model_id = substr(digest(RNAseq_data), 1, 6)
} else {
	model_id = params$model_id
}

CCLE_preds = read_rds(here('data/CCLE_prediction_summary.rds'))

predictions = predictions %>%
	left_join(CCLE_preds)

source(here('functions.R'))
```

```{r, include = F}
RNAseq_text = c()

if (dim(RNAseq_data)[1] > 100) {
	RNAseq_text = paste0("The data you submitted has ", dim(RNAseq_data)[1], " out of the 110 genes included in the model.")
} else if (dim(RNAseq_data)[1] < 100 & dim(RNAseq_data)[1] > 50) {
	RNAseq_text = paste0("The data you submitted has ", dim(RNAseq_data)[1], " out of the 110 genes included in the model. There was a problem with finding many of the genes in your data set. All genes missing from your data were filled with the average value from the cell lines in the CCLE. If you think this is an error, please get in touch with me through github (https://github.com/mbergins/kinase_inhibitor_pred_app).")
} else {
	RNAseq_text = paste0("The data you submitted has ", dim(RNAseq_data)[1], " out of the 110 genes included in the model. The system wasn't able to find a majority of the genes expected. All genes missing from your data were filled with the average value from the cell lines in the CCLE. The following predictions are not customized for your data.  If you think this is an error, please get in touch with me through github (https://github.com/mbergins/kinase_inhibitor_pred_app).")
}

```

This report summarizes the cell viability predictions for your data set. `r RNAseq_text` For reference, the system assigned your data the ID: `r model_id`.

# Cell Viability Predictions

To provide context for the predictions from your data, all of the following plots also show a summary of the predictions from the cell lines in the CCLE. The gray shaded region shows the range (95% coverage) of predictions for that compound, while the black line shows the average prediction. Predictions for your data appear as a blue line.

To help pick out potentially interesting compounds from the model predictions, we've sorted the predictions using four different methods:

* The compound is predicted to have minimal effects on cell viability.
* The compound is predicted to have high average effect on cell viability.
* The compound is predicted to show a wide range of effect on cell viability.
* The compound is predicted to vary from the CCLE average effect.

These categories are not mutually exclusive, so it's possible that a single compound will be present in multiple compound sets. Otherwise, the results are displayed as a set of small multiple graphs with the compound name in the title section.

```{r, include = F}
summary_results = predictions %>% 
	group_by(drug) %>%
	summarise(mean_via = mean(predicted_viability),
						CCLE_diff = abs(mean(predicted_viability - mean_via)),
						range_via = max(predicted_viability) - min(predicted_viability))
```

## Minimal Effects

```{r, echo = F}
low_eff_drugs = summary_results %>% arrange(desc(mean_via)) %>% slice(1:5) %>% pull(drug)
predictions %>%
	filter(drug %in% low_eff_drugs) %>%
	mutate(drug = fct_relevel(drug, low_eff_drugs)) %>%
	plot_pred_set()
```

## High Effects

```{r, echo = F}
high_eff_drugs = summary_results %>% arrange(mean_via) %>% slice(1:5) %>% pull(drug)
predictions %>%
	filter(drug %in% high_eff_drugs) %>%
	mutate(drug = fct_relevel(drug, high_eff_drugs)) %>%
	plot_pred_set()
```

## High Range of Effect

```{r, echo = F}
high_range_drugs = summary_results %>% arrange(desc(range_via)) %>% slice(1:5) %>% pull(drug)
predictions %>%
	filter(drug %in% high_range_drugs) %>%
	mutate(drug = fct_relevel(drug, high_range_drugs)) %>%
	plot_pred_set()
```

## Largest Difference from CCLE

```{r, echo = F}
ccle_diff_drugs = summary_results %>% arrange(desc(CCLE_diff), desc(range_via)) %>% slice(1:5) %>% pull(drug)
predictions %>%
	filter(drug %in% ccle_diff_drugs) %>%
	mutate(drug = fct_relevel(drug, ccle_diff_drugs)) %>%
	plot_pred_set()
```
